Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-06 doc/main_jfm.tex
some changes (fig captions)
some changes (conclusion,ref)

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two JP vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right JP vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}

@@

This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
hydrophobic interactions between lipids and hydrodynamic interactions.
The mobility problem using integral equation methods combines the previously introduced HAP and the 
revised hydrophobic force for obtaining particle dynamics.

The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
%
With the use of selected parameters, the numerical algorithm yields good qualitative results such as
phenomena in tank-treading JP vesicle. The reduced area $A^*$ decreases as the shear rate increases
 and we measure the equilibrium reduced area for a number of shear rates. The results show that the total
 length of JP vesicle is conserved and the decay rate of the reduced area is independent of shear rates when shear rates $\dot\gamma$ are between $\sim0.005$ ns$^{-1}$ and $0.008$ ns$^{-1}$.
Moreover, the proposed model can capture the membrane rupture when the shear flow is at a high shear rate
and this makes a breakthrough about having an idea for simulating such phenomenon different from other continuum modeling simulations when the bilayer membrane is represented as a closed and continuous curve.

@@

We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape. The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
state. A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}. An interesting outcome is that the mean
$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
may be caused by the granularity of the JP vesicle and choices of model parameters.

@@

Our future goal is to extend the current framework to a three-dimensional JP vesicle system. 
The further implementation of adding a fast algorithms such as the fast multipole method is also a 
practical approach.
Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.

>>>>

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
  where the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
  The background color is the fluid
  pressure. The color bar is identical for all panels. Streamlines are
  plotted in purple. The insets of all panels are generated from
  simulations of a continuum model of the vesicles and the streamlines
  agree between the two models. }
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two JP vesicles suspended in an
  extensional flow where the dimensioneless extensional rate is
  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
  above the $x$-axis and the centroid of the right JP vesicle is
  $0.1$ units below the $x$-axis. The initial configuration is shown in
  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
  The background color is the fluid pressure. The color bar
  is identical for all panels. Streamlines are plotted in purple. The
  insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the models.}
\end{figure}

@@

This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
hydrophobic interactions between coarse-grained lipids and hydrodynamic interactions.
The hydrophobic interactions exhibit the self-assembly property of the lipid bilayer menbrane different from
the pair-particle interactions adopted in molecular dynamics simulations. 
The proposed energy potential combining with the mobility problems for rigid body motion leads to capture membrane mechanics such as deformations, stretching modulus, and the permeability of JP membrane in a solvent. This work is highly applicable with fields in material science and condensed matter physics such as Janus colloid (\cite{Bradley2017,Mallory2017}) and the setup can be easily tuned to match the experiments, 
for instance, morphology of colloid surfactants. (\cite{Bradley2016})

The mobility problem using integral equation methods combines the previously introduced HAP and the 
revised hydrophobic force for obtaining particle dynamics. 
The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
%
With the use of selected parameters, the numerical algorithm yields good qualitative results such as
phenomena in tank-treading JP vesicle. The reduced area $A^*$ decreases as the shear rate increases
 and we measure the equilibrium reduced area for a number of shear rates. The results show that the total
 length of JP vesicle is conserved and the decay rate of the reduced area is independent of shear rates when shear rates $\dot\gamma$ are between $\sim0.005$ ns$^{-1}$ and $0.008$ ns$^{-1}$.
Moreover, the proposed model can capture the membrane rupture when the shear flow is at a high shear rate
and this makes a breakthrough about having an idea for simulating such phenomenon different from other continuum modeling simulations when the bilayer membrane is represented as a closed and continuous curve.

@@

We also study the spatial migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape. The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium state. A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}. An interesting outcome is that the mean $y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this may be caused by the granularity of the JP vesicle and choices of model parameters.

@@

Our future goal is to extend the current framework to a three-dimensional JP vesicle system. 
The further implementation of adding a fast algorithms such as the fast multipole method is also a 
practical approach.
One ongoing work is to add thermal fluctuations onto Janus particles to obtain Brownian dynamics is crucial for obtaining membrane diffusion.
Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.
